---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rscontract

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/edgararuiz/rscontract.svg?branch=master)](https://travis-ci.org/edgararuiz/rscontract)
[![Codecov test coverage](https://codecov.io/gh/edgararuiz/rscontract/branch/master/graph/badge.svg)](https://codecov.io/gh/edgararuiz/rscontract?branch=master)
<!-- badges: end -->

It is main goal is make it easier for other R packages or R projects to integrate with the RStudio Connections Contract.  It provides two levels to integrate with the Connections pane:

1. `rscontract_spec()` (higher) - A function that enables the user pass a hierarchical list object to describe the structure of the connection (catalog/schema/table).  It is design in a way that the defaults open a very simple connection without changing any arguments.  The idea is to allow you to easily iterate through small argument changes as you are learning how it works. 
1. `rscontract_ide()` (lower) - The arguments of this function matches one-to-one with the expected entries needed to open a Connection pane. 

There are three functions that actually interact with the RStudio IDE:

1. `rscontract_open()`  - Opens the Connection pane
1. `rscontract_update()` - Refreshes the Connections pane
1. `rscontract_close()` - Closes the Connections pane

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("edgararuiz/rscontract")
```

## Basic example

The stock output of `rscontract_spec()` is loaded into a variable `spec`.  This way it is possible to display its contents before using it to open a new connection.

```{r setup}
library(rscontract)
```


```{r}
library(rscontract)
spec <- rscontract_spec()
str(spec)
```

The connection can now be opened with `spec`.

```{r}
rscontract_open(spec)
```

Notice above the values of the `type` and `host` entries inside `spec`. Those are the two pieces of information needed by RStudio to identify the connection that needs to be updated, or closed. 

```{r}
rscontract_update("spec_host", "spec_type")
```

After closing the connection, the content from the `connect_script` variable can be seen. 

```{r example}
rscontract_close("spec_host", "spec_type")
```

## Modified spec

```{r}
library(rscontract)
spec <- rscontract_spec(
  type = "my_type",
  host = "my_host", 
  icon = system.file("images", "rstudio-icon.png", package = "rscontract"),
  name = "Modified Name",
  connect_script = "[This is my connection code]",
  disconnect_code = "function() rscontract_close('my_host', 'my_type')",
  preview_code = "function(catalog, schema, table, limit) data.frame(catalog, schema, table, limit)"
)
str(spec)
```

```{r}
rscontract_open(spec)
```

## Action buttons

```{r}
spec$actions <- list(
  "Button 1" = list(
    icon = system.file("images", "rstudio-icon.png", package = "rscontract"),
    callback = function() print("hello")
  )
)

rscontract_open(spec)
```

```{r}
spec_function <- function(x, message) {
  x$actions <- list(
  "Button 1" = list(
    icon = system.file("images", "rstudio-icon.png", package = "rscontract"),
    callback = function() print(message)
  ))
  x
}

rscontract_open(spec_function(spec, "test"))
```


```{r}
rscontract_close("my_host", "my_type")
```

## Catalog structure

```{r}
str(sample_catalog())
```

```{r}
my_cat <- sample_catalog()
my_cat$catalogs$schemas$tables$fields[[3]] <- list(name = "test", type = "int")
spec <- rscontract_spec()
spec$catalog_list <- my_cat
str(spec)
rscontract_open(spec)
```


## From a file

```{r}
contract_file <- system.file("specs", "simple.yml", package = "rscontract")
contract <- yaml::read_yaml(contract_file)
str(contract)
```

```{r}
spec <- as_rscontract(contract)
rscontract_open(spec)
```

```{r}
#contract_file <- system.file("specs", "full.yml", package = "rscontract")
contract_file <- "inst/specs/full.yml"
contract <- yaml::read_yaml(contract_file)
str(contract)
```

```{r}
my_fields <- function() list(name = "ext_function", type = "int")
spec <- as_rscontract(contract)
rscontract_open(spec)
```


