---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rscontract

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/edgararuiz/rscontracts.svg?branch=master)](https://travis-ci.org/edgararuiz/rscontracts)
[![Codecov test coverage](https://codecov.io/gh/edgararuiz/rscontracts/branch/master/graph/badge.svg)](https://codecov.io/gh/edgararuiz/rscontracts?branch=master)
<!-- badges: end -->

Provides a generic implementation of the RStudio Connection Contract to make it easier for database connections, and other type of connections, opened via R packages integrate with the Connections Pane inside the RStudio IDE.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("edgararuiz/rscontracts")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rscontract)

con <- rscontract_open(rscontract_spec())

rscontract_update(con)

rscontract_close(con)
```
