---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)

add_figure <- function(path, width = 400) {
  char_html <- paste0("<img src='", path,"' width ='", width,"px'/><br/>")
  htmltools::HTML(char_html)
}

toc <- function() {
  re <- readLines("README.Rmd")
  has_title <- as.logical(lapply(re, function(x) substr(x, 1, 2) == "##"))
  only_titles <- re[has_title]
  titles <- trimws(gsub("#", "", only_titles))
  links <- trimws(gsub("`", "", titles))
  links <- tolower(links)
  links <- trimws(gsub(" ", "-", links))
  toc_list <- lapply(
    seq_along(titles),
    function(x) {
      pad <- ifelse(substr(only_titles[x], 1, 3) == "###", "    - ", "  - ")
      paste0(pad, "[", titles[x], "](#",links[x], ")")
    }
  )
  toc_full <- paste(toc_list, collapse = "\n") 
  cat(toc_full)
}
```


# rscontract

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/edgararuiz/rscontract.svg?branch=master)](https://travis-ci.org/edgararuiz/rscontract)
[![Codecov test coverage](https://codecov.io/gh/edgararuiz/rscontract/branch/master/graph/badge.svg)](https://codecov.io/gh/edgararuiz/rscontract?branch=master)
<!-- badges: end -->

  - [Intro](#intro)
  - [Functions](#functions)
  - [Installation](#installation)
  - [Examples](#examples)
    - [Basic example](#basic-example)
    - [Modified spec](#modified-spec)
    - [Action buttons](#action-buttons)
    - [From a file](#from-a-file)
    - [R code as a value](#r-code-as-a-value)
    - [More than one schema](#more-than-one-schema)

## Intro

Makes it easier for other R packages or R projects to integrate with the RStudio Connections Contract.  It provides several options to describe the structure of your connection.  One of the options provided by `rscontract` is to use a YAML file that can contain the structure of the connection, and easily convert that into a proper RStudio Connections contract with a couple of lines of code: 

`r add_figure("man/figures/yamltocontract.png", 1000)`

## Functions

It provides two levels of integration abstraction with the Connections pane:

1. `rscontract_spec()` (higher) - Enables the user to pass a hierarchical list to describe the structure of the connection (catalog/schema/table).  The defaults are setup so you can open a very simple connection without changing any arguments.  The idea is to allow you to easily iterate through small argument changes as you are learning how the Connection pane works. 
1. `rscontract_ide()` (lower) - The arguments of this function matches one-to-one with the expected entries needed to open a Connection pane. 

The `as_rscontract()` function converts a variable into the same format that `rscontract_ide()` returns.  This makes it possible for objects such as `list`s returned by `yaml::read_yaml()` to work. 

There are three functions that actually interact with the RStudio IDE:

1. `rscontract_open()`  - Opens the Connection pane. It requires a properly formatted Connections pane provided by the `rscontract_spec()`, `rscontract_ide()`, or `as_rscontract()` functions.
1. `rscontract_update()` - Refreshes the already opened Connections pane
1. `rscontract_close()` - Closes the Connections pane.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("edgararuiz/rscontract")
```

## Examples

### Basic example

The stock output of `rscontract_spec()` is loaded into a variable `spec`.  This way it is possible to display its contents before using it to open a new connection.  

```{r setup}
library(rscontract)
```


```{r}
library(rscontract)

spec <- rscontract_spec()
str(spec)
```

The connection can now be opened with `spec`.

```{r}
rscontract_open(spec)
```

Notice above the values of the `type` and `host` entries inside `spec`. Those are the two pieces of information needed by RStudio to identify the connection that needs to be updated, or closed. 

`r add_figure("man/figures/open-1.png", 400)`

`rscontract` comes with a basic example accessible via the `sample_catalog()` function.  By default, `rscontract_spec()` uses `sample_catalog()` in the `object_types` entry to automatically give you working sample Connections pane.

```{r}
rscontract_update("spec_host", "spec_type")
```

After closing the connection, the content from the `connect_script` variable can be seen. 

```{r example}
rscontract_close("spec_host", "spec_type")
```

`r add_figure("man/figures/closed-1.png", 400)`

### Modified spec

To start creating your own connection setup, simply modify the arguments in `rscontract_spec()` that you wish to test.  Here is an example of a few modifications that are possible to make: 

```{r}
spec <- rscontract_spec(
  type = "my_type",
  host = "my_host", 
  icon = system.file("images", "rstudio-icon.png", package = "rscontract"),
  name = "Modified Name",
  connect_script = "[This is my connection code]",
  disconnect_code = "function() rscontract_close('my_host', 'my_type')",
  preview_code = "function(catalog, schema, table, limit) data.frame(catalog, schema, table, limit)"
)

rscontract_open(spec)
```

`r add_figure("man/figures/modified.png", 800)`

### Action buttons

The Connections pane also give you the ability to add custom buttons at the top of the pane.  These can be setup to run a specific R instruction once clicked. To add them simply modify the `action` entry in the spec.   In the example below, "hello" is sent to the R Console when 'Button 1' is clicked.

```{r}
spec$actions <- list(
  "Button 1" = list(
    icon = system.file("images", "rstudio-icon.png", package = "rscontract"),
    callback = function() print("hello")
  )
)

rscontract_open(spec)
```

`r add_figure("man/figures/button-1.png", 400)`

```r
#> rscontract_open(spec)
#> [1] "hello"
```

To add flexibility, wrap the list preparation inside a function:

```{r}
spec_function <- function(x, message) {
  x$actions <- list(
  "Button 1" = list(
    icon = system.file("images", "rstudio-icon.png", package = "rscontract"),
    callback = function() print(message)
  ))
  x
}

rscontract_open(spec_function(spec, "test"))
```

```r
#> rscontract_open(spec_function(spec, "test"))
#> [1] "test"
```

```{r}
rscontract_close("my_host", "my_type")
```

### From a file

A YAML file can be used to create the connection.  The structure and name of each field has to match to what is expected by `rscontract`.  The example below shows a basic example of the names and the expected type of input.  By default, the content in the following fields will be evaluated is if it was R code:

- `disconnect_code`
- `preview_code`

Here is an sample file included as part of the `rscontract` package:

```yaml
name: My Connection
type: my_connection
host: hosted_here
connect_script: my_function_connect(path = "myfile.txt")
disconnect_code:  function() rscontract_close("hosted_here", "my_connection")
preview_code: function(table, view, ...) c(table, view)
catalog_list:
  catalogs:
    name: my_catalog
    type: catalog
    schemas:
      - name: my_schema
        type: schema
        tables:
          - name: my_table
            type: table
            fields:
              - name: field1
                type: nbr
              - name: field2
                type: chr
```

The key of using a YAML file, is to coerce it into a contract format using `as_rscontract()`. Then use `rscontract_open()` to start the connection.

```{r}
# Obtains the path to the sample YAML file
contract_file <- system.file("specs", "simple.yml", package = "rscontract")
# Reads the YAML file using the `yaml` package
contract <- yaml::read_yaml(contract_file)
# Coerces list into a contract spec
spec <- as_rscontract(contract)
# Opens the connection
rscontract_open(spec)
```

`r add_figure("man/figures/yaml-1.png", 400)`

### R code as a value

In order to pass R code instead of the value, then use a sub-entry called `code` for the entry you wish to modify. 

```yaml
name:
  code: toupper("my_title")
type:
  code: tolower("TYPE")
host: host
connect_script: Place connection code here
disconnect_code:  function() rscontract_close("host", "type")
preview_code: function(table, view, ...) c(table, view)
catalog_list:
  catalogs:
    name: my_catalog
    type: catalog
    schemas:
      - name: my_schema1
        type: schema
        tables:
          - name: my_view1
            type: view
            fields:
              code: list(list(name = "ext_function", type = "int"))
```

```{r, eval = FALSE}
contract_file <- system.file("specs", "full.yml", package = "rscontract")
contract <- yaml::read_yaml(contract_file)
spec <- as_rscontract(contract)
rscontract_open(spec)
```

`r add_figure("man/figures/yaml-2.png", 400)`


### More than one schema

Here is an example of a Contract with multiple Schemata:

```yaml
name: displayName
type: type
host: host
connect_script: Place connection code here
disconnect_code:  function() rscontract_close("host", "type")
preview_code: function(table, view, ...) c(table, view)
catalog_list:
  catalogs:
    name: my_catalog
    type: catalog
    schemas:
      - name: my_schema1
        type: schema
        tables:
          - name: my_table1
            type: table
            fields:
              - name: field1
                type: nbr
              - name: field2
                type: chr
          - name: my_view1
            type: view
            fields:
              - name: field3
                type: nbr
              - name: field4
                type: chr
      - name: my_schema2
        type: schema
        tables:
          - name: my_table4
            type: table
            fields:
              - name: field5
                type: nbr
              - name: field6
                type: chr
          - name: my_view2
            type: view
            fields:
              - name: field7
                type: nbr
              - name: field8
                type: chr
```

```{r, eval = FALSE}
contract_file <- system.file("specs", "two-schemas.yml", package = "rscontract")
contract <- yaml::read_yaml(contract_file)
spec <- as_rscontract(contract)
rscontract_open(spec)
```

`r add_figure("man/figures/yaml-3.png", 400)`
